---
title: "Background selection in maize and humans"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---

```{r setup}
knitr::opts_knit$set(root.dir = '../')
```

For maize, we simulated data from $N_e=10,000$ with bottleneck and growth following [Beissinger et al. 2016](https://www.nature.com/articles/nplants201684). 
For Europeans, we follow a slightly modified model of [Torres et al. 2017](http://www.biorxiv.org/content/early/2017/09/01/181859) that excludes the ancestral expansion, and scales ancestral $N_e=10,000$, but the gene model is as above. 

We simulate neutral $\pi$ and $\xi_1$ (singletons) shown every 100 generations in each of 24 4Kb windows centered around a 4kb "gene" which has neutral (\frac{1}{4}) and deleterious (\frac{3}{4}) mutations. We run simulations with and without background selection.  To simulate background selection we draaw deleterious mutations from a gamma distribution with some mean s (see below). 

For each parameter set (select $\times$ statistic $\times$ demography) we then want to test the effect of generation and genetation $\times$ window on the statistic and do so with a simple ANOVA.

#Boring Libraries and functions

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggjoy)
library(viridis)
library(cowplot)
```

Read in data from pylibseq.

```{r munge function}
read_sim<-function(pidata,xidata,neutral=FALSE){
  #read data
  pi<-as.tibble(read.csv(pidata,header=F))
  pi<-mutate(pi,stat=rep("pi",length(pi[,1])))
  xi<-as.tibble(read.csv(xidata,header=F)) 
  xi<-mutate(xi,stat=rep("xi",length(xi[,1])))
  #munge into single tibble of means
  data<-rbind(xi,pi) %>%
    `colnames<-`(c("gen", 1:25, "sim", "stat")) %>%
    gather(window,value,2:26) %>% 
    mutate(gen=gen-100000) %>%
    group_by(gen,stat,window) %>%
    summarize(mean_val=mean(value)) %>%
    mutate(window=(as.numeric(window)-13)*4000*3E-5,mean_val=mean_val)
    data=mutate(data,mean_val=if_else(window==0.00,mean_val*4,mean_val))
  if(neutral==TRUE){
    data=mutate(data,mean_val=if_else(window==0.00,mean_val/4,mean_val))
  }
  return(data)
}
```

Read in only a single simulation rather than means. For ANOVA later.
```{r single sim munge}
read_single_sim<-function(pidata,xidata,neutral=FALSE){
  #read data
  pi<-as.tibble(read.csv(pidata,header=F))
  pi<-mutate(pi,stat=rep("pi",length(pi[,1])))
  xi<-as.tibble(read.csv(xidata,header=F)) 
  xi<-mutate(xi,stat=rep("xi",length(xi[,1])))
  #munge into single tibble of means
  data<-rbind(xi,pi) %>%
    `colnames<-`(c("gen", 1:25, "sim", "stat")) %>%
    gather(window,value,2:26) %>% 
    mutate(gen=gen-100000) %>%
    mutate(window=(as.numeric(window)-13)*4000*3E-5)
    data=mutate(data,value=if_else(window==0.00,value*4,value))
  if(neutral==TRUE){
    data=mutate(data,value=if_else(window==0.00,value/4,value))
  }
  return(data)
}
```


Merge data with BGS with a neutral sim to standardize.
```{r merge}
merge_sel_neutral <- function(sel_sim_data,neut_sim_data){
  merged <- merge(sel_sim_data,neut_sim_data,by=c('gen','stat','window'))
  merged$mean_val <- merged$mean_val.x/merged$mean_val.y
  merged
}

```

Merge individual BGS sims with paired neutral sim.
```{r merge single}
merge_single_sel_neutral <- function(sel_sim_data,neut_sim_data){
  merged <- merge(sel_sim_data,neut_sim_data,by=c('gen','sim','stat','window'))
  merged$value <- merged$value.x/merged$value.y
  merged
}
```

ANOVA on sim results.
```{r anova function}
sim_anova <- function(somedata,stats){
  sep_parm <- filter(somedata,stat==stats,!is.na(value),value != Inf)
  sep_parm$gen <- as.factor(sep_parm$gen)
  sep_parm$window <- as.factor(sep_parm$window)
  fit <- lm(value ~ gen + window + gen*window, data=sep_parm,na.action = na.exclude)

  print(anova(fit))
}
```


Plot data
```{r plot_fun}
simplot<-function(somedata,mystat,label,bneck){
  ggplot(filter(somedata,gen %% 100 <1,stat==mystat,gen>bneck), aes(x=window, y=mean_val, group = gen,color=gen)) + 
  scale_color_viridis(name='Generation') +   
  background_grid(major = "xy", minor = "none") +
  geom_line() + 
  ylab(label)  + xlab("cM") +
  scale_x_continuous(breaks = seq(-1.5,1.5,0.5))
}
```

# Neutral Sims

### Maize
```{r}
maize_neutral <-read_sim("sims/results/sim_neutralPi_maize_neutral2.csv","sims/results/sim_singleton_maize_neutral2.csv",neutral=TRUE)
maize_neutral_anova <-read_single_sim("sims/results/sim_neutralPi_maize_neutral2.csv","sims/results/sim_singleton_maize_neutral2.csv",neutral=TRUE)
simplot(maize_neutral,"pi",expression(bar(pi)),2200)
```

### European
```{r}
European_neutral <-read_sim("sims/results/sim_neutralPi_European_neutral2.csv","sims/results/sim_singleton_European_neutral2.csv",neutral=TRUE)
European_neutral_anova <-read_single_sim("sims/results/sim_neutralPi_European_neutral2.csv","sims/results/sim_singleton_European_neutral2.csv",neutral=TRUE)
simplot(European_neutral,"pi",expression(bar(pi)),2200)
```

# Weak selection 
Set mean to $s=5\times 10^{-5}$

###Maize
```{r}
maize<-read_sim("sims/results/sim_neutralPi_maize_s5E-5.csv","sims/results/sim_singleton_maize_s5E-5.csv")
maize_anova<-read_single_sim("sims/results/sim_neutralPi_maize_s5E-5.csv","sims/results/sim_singleton_maize_s5E-5.csv")
maize_merged <- merge_sel_neutral(maize,maize_neutral)
maize_merged_anova <- merge_single_sel_neutral(maize_anova,maize_neutral_anova)
```

$\pi$
```{r}
simplot(maize_merged,"pi",expression(bar(pi)/bar(pi)[neut]),2200)
sim_anova(maize_merged_anova,'pi')
```

$\xi_1$
```{r}
simplot(maize_merged,"xi",expression(bar(xi[i])/bar(xi[i[neut]])),2200)
sim_anova(maize_merged_anova,'xi')
```

### Human

```{r}
European<-read_sim("sims/results/sim_neutralPi_European_s5E-5.csv","sims/results/sim_singleton_European_s5E-5.csv")
European_merged <- merge_sel_neutral(European,European_neutral)
European_anova<-read_single_sim("sims/results/sim_neutralPi_European_s5E-5.csv","sims/results/sim_singleton_European_s5E-5.csv")
European_merged_anova <- merge_single_sel_neutral(European_anova,European_neutral_anova)
```

$\pi$
```{r}
simplot(European_merged,"pi",expression(bar(pi)/bar(pi)[neut]),100)
sim_anova(European_merged_anova,'pi')
```

$\xi_1$
```{r}
simplot(European_merged,"xi",expression(bar(xi[i])/bar(xi[i[neut]])),100)
sim_anova(European_merged_anova,'xi')
```

#Intermediate selection 
$s=5\times 10^{-4}$

###Maize
```{r}
maize<-read_sim("sims/results/sim_neutralPi_maize_s5E-4.csv","sims/results/sim_singleton_maize_s5E-4.csv")
maize_anova<-read_single_sim("sims/results/sim_neutralPi_maize_s5E-4.csv","sims/results/sim_singleton_maize_s5E-4.csv")
maize_merged <- merge_sel_neutral(maize,maize_neutral)
maize_merged_anova <- merge_single_sel_neutral(maize_anova,maize_neutral_anova)
```

$\pi$
```{r}
simplot(maize_merged,"pi",expression(bar(pi)/bar(pi)[neut]),2200)
sim_anova(maize_merged_anova,'pi')
```

$\xi_1$
```{r}
simplot(maize_merged,"xi",expression(bar(xi[i])/bar(xi[i[neut]])),2200)
sim_anova(maize_merged_anova,'xi')
```

### Human

```{r}
European<-read_sim("sims/results/sim_neutralPi_European_s5E-4.csv","sims/results/sim_singleton_European_s5E-4.csv")
European_merged <- merge_sel_neutral(European,European_neutral)
European_anova<-read_single_sim("sims/results/sim_neutralPi_European_s5E-4.csv","sims/results/sim_singleton_European_s5E-4.csv")
European_merged_anova <- merge_single_sel_neutral(European_anova,European_neutral_anova)
```

$\pi$
```{r}
simplot(European_merged,"pi",expression(bar(pi)/bar(pi)[neut]),100)
sim_anova(European_merged_anova,'pi')
```

$\xi_1$
```{r}
simplot(European_merged,"xi",expression(bar(xi[i])/bar(xi[i[neut]])),100)
sim_anova(European_merged_anova,'xi')
```

# Strong selection 

$s=5\times 10^{-3}$

###Maize
```{r}
maize<-read_sim("sims/results/sim_neutralPi_maize_s5E-3.csv","sims/results/sim_singleton_maize_s5E-3.csv")
maize_anova<-read_single_sim("sims/results/sim_neutralPi_maize_s5E-3.csv","sims/results/sim_singleton_maize_s5E-3.csv")
maize_merged <- merge_sel_neutral(maize,maize_neutral)
maize_merged_anova <- merge_single_sel_neutral(maize_anova,maize_neutral_anova)
```

$\pi$
```{r}
simplot(maize_merged,"pi",expression(bar(pi)/bar(pi)[neut]),2200)
sim_anova(maize_merged_anova,'pi')
```

$\xi_1$
```{r}
simplot(maize_merged,"xi",expression(bar(xi[i])/bar(xi[i[neut]])),2200)
sim_anova(maize_merged_anova,'xi')
```

### Human

```{r}
European<-read_sim("sims/results/sim_neutralPi_European_s5E-3.csv","sims/results/sim_singleton_European_s5E-3.csv")
European_merged <- merge_sel_neutral(European,European_neutral)
European_anova<-read_single_sim("sims/results/sim_neutralPi_European_s5E-3.csv","sims/results/sim_singleton_European_s5E-3.csv")
European_merged_anova <- merge_single_sel_neutral(European_anova,European_neutral_anova)
```

$\pi$
```{r}
simplot(European_merged,"pi",expression(bar(pi)/bar(pi)[neut]),100)
sim_anova(European_merged_anova,'pi')
```

$\xi_1$
```{r}
simplot(European_merged,"xi",expression(bar(xi[i])/bar(xi[i[neut]])),100)
sim_anova(European_merged_anova,'xi')
```